%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{soul}
\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Shuguang} % Your first name
\familyname{Han} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{}
\address{4740 Baum Boulevard, Pittsburgh, PA}{}
\mobile{Contact: 412-736-4275}
\email{hanshuguang@gmail.com}
\homepage{www.pitt.edu/~shh69}{http://www.pitt.edu/$\sim$shh69} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
% \photo[70pt][0.4pt]{pictures/daniele} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\textbf{Education}}

\cvitem{2011 -- 2017}{\textbf{University of Pittsburgh}, Pittsburgh, PA, United States}
\cvitem{}{\textbf{Doctoral Student}, Advisor: \textit{Dr. Daqing He} \& \textit{Dr. Peter Brusilovsky}}
\cvitem{}{\textit{Research}: Interactive Information Retrieval, People Search, Collaborative Search}
\vspace{1em}

\cvitem{2004 -- 2010}{\textbf{Wuhan University}, Wuhan, Hubei, China}
\cvitem{}{\textbf{Bachelor \& Master Student}, Advisor: \textit{Dr. Wei Lu}}
\cvitem{}{\textit{Research}: Information Retrieval, Expert Search}
\vspace{1em}

%\section{Masters Thesis}

%\cvitem{Title}{\emph{Technologies and characterization of ferroelectric polymers for biomedical sensors}}
%\cvitem{Supervisors}{Professor Antonino Fiorillo}
%\cvitem{Description}{This thesis is based on the implementation of a temperature sensor.}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\textbf{Work Experience}}

\cventry{2017 -- Now}{Google Research}{Software Engineer}{Mountain View}{CA, United States}{}
\vspace{1em}

\cventry{2015 -- 2015}{Google Research}{Intern}{Mountain View}{CA, United States}
{Project: mobile gaze attention tracking with front-facing camera.}
\vspace{1em}

\cventry{2015 -- 2015}{Yahoo! Labs}{Intern Scientist}{Sunnyvale}{CA, United States}
{Project: mobile search session understanding}
\vspace{1em}

\cventry{2014 -- 2014}{Google}{Intern}{Mountain View}{CA, United States}
{Project: behavior-based crowdsourcing quality control.}
\vspace{1em}

% \cventry{2013 -- 2013}{Columbia University}{Research Intern}{}{New York, NY, United States}
% {}
% \vspace{0.5em}

% \cventry{2012 -- 2012}{Carnegie Mellon University}{Research Intern}{}{Pittsburgh, PA, United States}
% {}
% \vspace{0.5em}

\cventry{2009 -- 2009}{Baidu}{Product Manager}{}{Beijing, China}
{}
\vspace{1em}

%------------------------------------------------

\section{\textbf{Selected Publications}}

\cvitem{ACL 2017}{Rui Meng, Sanqiang Zhao, \textbf{Shuguang Han}, Daqing He, Peter Brusilovsky and Yu Chi. 2017. \ul{Deep Keyphrase Generation}. In Annual Meeting of the Association for Computational Linguistics (ACL 2017). (To Appear)}
\vspace{1em}

\cvitem{CIKM 2016}{\textbf{Shuguang Han}, Xing Yi, Zhen Yue, Zhigeng Geng, and Alyssa Glass. 2016. \ul{Framing Mobile Information Needs:} An Investigation of Hierarchical Query Sequence Structure. In Proceedings of the 25th ACM International on Conference on Information and Knowledge Management. ACM, New York, NY, USA, 2131-2136.}
\vspace{1em}

\cvitem{CHIIR 2016}{\textbf{Shuguang Han}, Daqing He, Zhen Yue, and Jiepu Jiang. 2016. \ul{Contextual Support for Collaborative Information Retrieval}. In Proceedings of the 2016 ACM on Conference on Human Information Interaction and Retrieval. ACM, New York, NY, USA, 33-42.}
\vspace{1em}

\cvitem{TIST 2016}{\textbf{Shuguang Han}, Peng Dai, Praveen Paritosh, and David Huynh. 2016. \ul{Crowdsourcing Human Annotation on Web Page Structure:} Infrastructure Design and Behavior-Based Quality Control. ACM Transaction on Intelligent System \& Technology. 7, 4, Article 56 (April 2016), 25 pages.}
\vspace{1em}

\cvitem{TOIS 2015}{\textbf{Shuguang Han}, Zhen Yue, and Daqing He. 2015. \ul{Understanding and Supporting Cross-Device Web Search for Exploratory Tasks with Mobile Touch Interactions}. ACM Transaction on Information System. 33, 4, Article 16 (April 2015), 34 pages.}
\vspace{1em}

\cvitem{IUI 2015}{Jae-wook Ahn, Peter Brusilovsky, and \textbf{Shuguang Han}. 2015. \ul{Personalized Search: Reconsidering the Value of Open User Models}. In Proceedings of the 20th International Conference on Intelligent User Interfaces (IUI '15). ACM, New York, NY, USA, 202-212.}
\vspace{1em}

\cvitem{UMAP 2015}{\textbf{Shuguang Han}, Daqing He, Zhen Yue, and Peter Brusilovsky. \ul{Supporting cross-device web search with social navigation-based mobile touch interactions}. In International Conference on User Modeling, Adaptation, and Personalization, pp. 143-155. Springer International Publishing, 2015.}
\vspace{1em}

\cvitem{CSCW 2014}{Zhen Yue, \textbf{Shuguang Han}, and Daqing He. 2014. \ul{Modeling search processes using hidden states in collaborative exploratory web search}. In Proceedings of the 17th ACM conference on Computer supported cooperative work \& social computing (CSCW '14). ACM, New York, NY, USA, 820-830.}
\vspace{1em}

\cvitem{CIKM 2013}{\textbf{Shuguang Han}, Daqing He, Jiepu Jiang, and Zhen Yue. 2013. \ul{Supporting exploratory people search: a study of factor transparency and user control}. In Proceedings of the 22nd ACM international conference on Information \& Knowledge Management (CIKM '13). ACM, New York, NY, USA, 449-458.}
\vspace{1em}

\cvitem{SBP 2013}{\textbf{Shuguang Han}, Daqing He, Peter Brusilovsky, and Zhen Yue. 2013. \ul{Coauthor prediction for junior researchers}. In Proceedings of the 6th international conference on Social Computing, Behavioral-Cultural Modeling and Prediction (SBP'13), 274-283. }
\vspace{1em}

\cvitem{HCIR 2012}{Jiepu Jiang, \textbf{Shuguang Han}, Jia Wu and Daqing He. \ul{IRIS-IPS: An Interactive People Search System for HCIR Challenge}. In Symposium on Human-Computer Interaction and Information Retrieval. 2012. [\textit{The Second Best Performance in HCIR Challenge}]}
\vspace{1em}

\cvitem{TREC 2011}{Jiepu Jiang, \textbf{Shuguang Han}, Jia Wu and Daqing He. \ul{PITT at TREC 2011 Session Track}. In Text REtrieval Conference (TREC). 2011. [\textit{The Best Performance in TREC Session Track}]}
\vspace{1em}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{\textbf{Other Publications}}

\cvitem{UMAP 2016}{Yun Huang, Michael Yudelson, \textbf{Shuguang Han}, Daqing He, and Peter Brusilovsky. 2016. \ul{Dynamic Knowledge Modeling in Textbook-Based Learning}. In Proceedings of the 2016 Conference on User Modeling Adaptation and Personalization (UMAP '16). ACM, New York, NY, USA, 141-150.}
\vspace{1em}

\cvitem{HMS 2016}{Chien, Shih-Yi, Michael Lewis, Siddharth Mehrotra, \textbf{Shuguang Han}, Nathan Brooks, Huadong Wang, and Katia Sycara. 2016. \ul{Task Switching for Supervisory Control of Multi-Robot Teams}. IEEE Transactions on Human-Machine Systems (2016).}
\vspace{1em}

\cvitem{Scientometrics 2016}{Lu Xiao, Guo Chen, Jianjun Sun, \textbf{Shuguang Han}, and Chengzhi Zhang. 2016. \ul{Exploring the topic hierarchy of digital library research in China using keyword networks}: a K-core decomposition approach. Scientometrics 108, 3 (September 2016), 1085-1101.}
\vspace{1em}

\cvitem{Computer 2014}{Zhen Yue, \textbf{Shuguang Han}, Daqing He, and Jiepu Jiang. 2014. \ul{Influences on Query Reformulation in Collaborative Web Search}. Computer. 47, 3 (March 2014), 46-53.}
\vspace{1em}

\cvitem{Electronic Library 2008}{Xiangxing Shen, Zhong Zheng, \textbf{Shuguang Han}, and Chong Shen. \ul{A review of the major projects constituting the China Academic Digital Library}. The Electronic Library 26, no. 1 (2008): 39-54.}
\vspace{1em}

\cvitem{ASIS\&T 2013}{Zhen Yue, \textbf{Shuguang Han}, and Daqing He. 2013. \ul{An investigation of the query behavior in task-based collaborative exploratory web search}. In Proceedings of the 76th ASIS\&T Annual Meeting: Beyond the Cloud: Rethinking Information Boundaries (ASIST '13), Andrew Grove (Ed.). American Society for Information Science, Silver Springs, MD, USA, , Article 77 , 10 pages.}
\vspace{1em}

\cvitem{SIGIR 2015 [Workshop]}{\textbf{Shuguang Han}, Daqing He, and Zhen Yue. \ul{Benchmarking the Privacy-Preserving People Search}. arXiv preprint arXiv:1409.5524 (2014).}
\vspace{1em}

\cvitem{iConference 2013 [Poster]}{\textbf{Shuguang Han}, Zhen Yue and Daqing He. 2013. \ul{Automatic detection of search tactic in individual information seeking: A Hidden Markov Model approach}. iConference 2013 Proceedings (pp. 712-716)}
\vspace{1em}

\cvitem{CIKM 2012 [Short]}{Zhen Yue, Jiepu Jiang, \textbf{Shuguang Han}, and Daqing He. 2012. \ul{Where do the query terms come from?: an analysis of query reformulation in collaborative web search}. In Proceedings of the 21st ACM international conference on Information and knowledge management (CIKM '12). ACM, New York, NY, USA, 2595-2598.}
\vspace{1em}

\cvitem{SIGIR 2012 [Poster]}{Jiepu Jiang, Zhen Yue, \textbf{Shuguang Han}, and Daqing He. 2012. \ul{Finding readings for scientists from social websites}. In Proceedings of the 35th international ACM SIGIR conference on Research and development in information retrieval (SIGIR '12). ACM, New York, NY, USA, 1075-1076.}
\vspace{1em}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{\textbf{Patent}}

\cvitem{2015}{Xing Yi, Zhen Yue, Alyssa Glass and \textbf{Shuguang Han}. Methods and Systems for Automatically Framing Mobile Search Information Need at Scale. 2015. To appear (at Yahoo! Labs).}
\vspace{1em}

\section{\textbf{Skills}}

\cvitem{Programing}{Java, JavaScript and Python (at Google), R, SPSS and Pig (at Yahoo!), Web Development (for Research Prototype)}
\vspace{1em}

\cvitem{Language}{Chinese (native), and English (fluent)}
\vspace{1em}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

%\section{Communication Skills}

%\cvitem{2010}{Oral Presentation at the California Business Conference}
%\cvitem{2009}{Poster at the Annual Business Conference in Oregon}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{\textbf{Services}}
\cvitem{Program}{2017: EMNLP and CIKM}
\cvitem{Committee}{2016: EMNLP and CIKM}
\cvitem{}{2015: EMNLP and SBP}
\cvitem{}{2014: SBP}

\vspace{1em}



\cvitem{Reviewers}{2017: WWW, SIGIR, EMNLP, IUI, CIKM and iConference}
\cvitem{}{2016: CIKM, EMNLP, WWW, IUI, UMAP, TOIS, IEEE TLT and IEEE Big Data.}
\cvitem{}{2015: WWW, KDD, EMNLP, HyperText, SBP, PLOS ONE and iConference}
\cvitem{}{2014: UMAP, HyperText, iConference and SBP}
\vspace{1em}
%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}

